\bibitem[\protect\citeauthoryear{McWilliams and Sloane}{1978}]{MS78}
MacWilliams, F.J. and Sloane, N.J.A.
\newblock {The Theory of Error-Correcting Codes, 2nd Edition}.

\bibitem[\protect\citeauthoryear{Berlekamp \bgroup \em et al. \egroup}{1978}]{BMT78}
E. Berlekamp, R. McEliece, and H. van Tilborg 
\newblock {On the inherent intractability of certain coding problems}.
\newblock In {\em Corresp. of IEEE}, 1978

\bibitem[\protect\citeauthoryear{Sang, Tian \bgroup \em et al.\egroup}{2005}]{TBK05}
Sang, Tian, Paul Beame, and Henry A. Kautz.
\newblock {Performing Bayesian inference by weighted model counting}.
\newblock In {\em Proc. of AAAI Vol.5}, 2005.

\bibitem[\protect\citeauthoryear{Guruswami \bgroup \em et al.\egroup}{2005}]{GV05}
Venkatesan Guruswami and Alexander Vardy
\newblock {Maximum-Likelihood Decoding
	of Reed-Solomon Codes is NP-hard}.
\newblock In Pages 470-478,Proc. of SODA, 2005 

\bibitem[\protect\citeauthoryear{Sinz}{2005}]{S05}
Carten Sinz
\newblock {Towards an Optimal CNF Encoding of
	Boolean Cardinality Constraints}.
\newblock In CP 2005 pp827-831.

\bibitem[\protect\citeauthoryear{Chavira \bgroup \em et al.\egroup}{2009}]{CD08}
Mark Chavira and Adnan Darwiche
\newblock {On probabilistic inference by weighted model counting}.
\newblock In {\em Proc. of AAAI},172(6-7): 772-779 2008.

\bibitem[\protect\citeauthoryear{Soos \bgroup \em et al.\egroup}{2009}]{SNC09}
Mate Soos, Karsten Nohl, and Claude Castelluccia.
\newblock {Extending {SAT} Solvers to Cryptographic Problems}.
\newblock In {\em Proc. of SAT}, 2009.

\bibitem[\protect\citeauthoryear{Gottlieb \bgroup \em et al.\egroup}{2012}]{GKM12}
Lee-Ad Gottlieb and Aryeh Kontorovich and Elchanan Mossel.
\newblock {VC bounds on the cardinality of nearly orthogonal function classes}.
\newblock In Discrete Math., 312(10): 1766–1775, 2012.

\bibitem[\protect\citeauthoryear{Belle \bgroup \em et al. \egroup}{2015}]{BBP15}
Vaishak Belle and Guy Van den Broeck and Andrea Passerini
\newblock {Hashing-Based Approximate Probabilistic Inference in Hybrid Domains}.
\newblock In {\em Proc. of IJCAI}, 2015

\bibitem[\protect\citeauthoryear{Dudek \bgroup \em et al. \egroup}{2016}]{DMV16}
Dudek, Jeffrey and  Meel, Kuldeep S. and  Vardi, Moshe Y.
\newblock {Combining the k-CNF and XOR Phase-Transitions}.
\newblock In {\em Proc. of IJCAI}, 2016

\bibitem[\protect\citeauthoryear{Dudek \bgroup \em et al. \egroup}{2017}]{DMV17}
Dudek, Jeffrey and  Meel, Kuldeep S. and  Vardi, Moshe Y.
\newblock {The Hard Problems Are Almost Everywhere For Random CNF-XOR Formulas}.
\newblock In {\em Proc. of IJCAI}, 2017

\bibitem[\protect\citeauthoryear{Duenas-Osorio \bgroup \em et al.\egroup}{2017}]{DMPV17}
Duenas-Osorio, Leonardo and  Meel, Kuldeep S. and  Paredes, Roger and  Vardi, Moshe Y.
\newblock {Counting-Based Reliability Estimation for Power-Transmission Grids}.
\newblock In {\em Proc. of AAAI}, 2017

\bibitem[\protect\citeauthoryear{Lagniez \bgroup \em et al.\egroup}{2017}]{LM17}
Jean-Marie Lagniez and Pierre Marquis,
\newblock {An Improved Decision-DNNF Compiler}.
\newblock In {\em Proc. of IJCAI}, 2017

\bibitem[\protect\citeauthoryear{Soos \bgroup \em et al.\egroup}{2019}]{SM19}
Soos, Mate and  Meel, Kuldeep S.
\newblock {BIRD: Engineering an Efficient CNF-XOR SAT Solver and its Applications to Approximate Model Counting}.
\newblock In {\em Proc. of AAAI}, 2019

